### 2019-03-21 4_implementation.tex
Add table listing systems.
More text in implementation.

We have implemented Task Bench in 13 parallel and distributed
programming languages and runtime systems. Below we describe the
systems, and any salient details of their Task Bench implementations.

In all cases, members of the respective programming systems' teams
were consulted during the development and evaluation of the
corresponding Task Bench implementations. Their insight was invaluable
in ensuring that we provide the highest level of quality in the Task
Bench implementations for each system.

>>>>

\input{t1_systems}

We have implemented Task Bench in the 13 parallel and distributed
programming systems listed in Table~\ref{tab:systems}. We describe the
systems, and any salient details of their Task Bench implementations,
below.

One challenge in implementing Task Bench for such a wide variety of
systems is that the capabilities of the systems vary considerably. For
example, some systems are \emph{implicitly parallel}, and provide some
form of parallelism discovery from sequential programs, whereas others
are \emph{explicitly parallel} and require users to specify the
parallelism in the program. As a rule of thumb we aim for the Task
Bench implementations to be represenative of how actual applications
would be written in the respective systems. Places where the Task
Bench implementations may be unidiomatic are noted below.

There are also aspects of some systems that we do not consider in our
evaluation. For example, a number of systems provide some level of
support for heterogeneous processors such as GPUs, but the support
varies so widely (if it exists at all) that it is challenging to come
up with a representative benchmark which allows these features to be
compared in an apples-to-apples manner.

In all cases, members of the respective programming systems' teams
were consulted during the development and evaluation of the
corresponding Task Bench implementations. Their insight was invaluable
to ensuring that we provide the highest level of quality in the Task
Bench implementations for each system.
